---
title: "Catastrophising Questionnaire open code"
output: 
  html_notebook:
    theme: united
    toc: yes
---

This code runs the analyses reported in the paper presenting a novel Catastrophising Questionnaire (Serfaty, Pike, Robinson). Before you run this code, please note the following:

1) This code depends on libraries/functions written by other users. These are all listed in the chunk below. Some parts of the code will not run without installing these packages/sourcing these functions. 

2) This code requires you to define a working directory, into which you should have already downloaded the data (from the 'Open code' folder in this OSF). This is done using the choose.dir() function, so will pop up automatically. 

3) This code will save images (the figures from the paper) into your working directory. If you do not want to do this, please enter 0 into the pop-up box. 


Load libraries that this depends on
```{r}
library('dplyr')
library('ggplot2')
library('lubridate')
library('paran')
library('psych')
library('corrr')
library('cowplot')
library('car')
library('reshape2')
library('pheatmap')
library('afex')
library('irr')
library('svDialogs')
library('nnet')
library('mirt')
library('semTools')
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
```

Set a working directory and define whether you want to save images

```{r}
workingdir=choose.dir()
save_images <- as.integer(dlgInput('Do you want to save images? 1=yes, 0=no: ', Sys.info()['0'])$res)
```


# Study 1 #

Load in the data

```{r}
data1<-read.csv(paste0(workingdir,'/experiment1.csv'))
```

Check how long the total experiment and questionnaire took
```{R}
cat_time_taken<-mean(data1$cat_questionnaire_time)
seconds_to_period(cat_time_taken/1000)

full_time_taken<-mean(data1$total_time)
seconds_to_period(full_time_taken)

data1_items<-data1[,c('X1','X2','X3','X4','X5','X6','X7','X8','X9','X10','X11','X12','X13','X14','X15','X16','X17','X18','X19','X20','X21','X22','X23','X24','X25','X26','X27','X28','X29','X30','X31')]

```

Do alpha, omega and inter-item and item-total correlations

```{r}
#alpha
psych::alpha(x=data1_items)

#omega
psych::omega(data1_items)

#inter-item correlation
data_correlation1 <- data1_items %>% corrr::correlate() 
data_correlation1 <- data_correlation1 %>% dplyr::select(-rowname) %>% colMeans(na.rm = TRUE)
data_correlation1
mean(data_correlation1)

data.frame(data_correlation1) %>% 
  ggplot2::ggplot(aes(x = data_correlation1)) +
  geom_histogram(bins = 10, alpha = .5) +
  geom_vline(xintercept = mean(data_correlation1), color = "red") +
  xlab("Mean inter-item correlation") +
  theme_bw()

#plot item response distributions
data_melted <- melt(data1_items)
plot<-ggplot(data_melted,aes(x = value, group = variable)) +
geom_bar()
plot+facet_wrap(. ~ variable)

#item-total correlation
data1_items$score<-rowSums(data1_items)
total_correlation1 <- data1_items %>% corrr::correlate() %>% focus(score)
mean(total_correlation1$score)

```
Run an EFA and obtain the parameters recorded

```{r}
data1_items<- data1_items %>% dplyr::select(-'score')

psych::KMO(data1_items)
temp<-round(cor(data1_items),2)
cortest.bartlett(temp,n=nrow(data1_items))


parallel1 <- fa.parallel(data1_items, fm = 'minres', fa = 'fa')

efa1<- fa(data1_items,nfactors = parallel1$nfact,rotate = "oblimin",fm="minres")
print(efa1)
```
Item response theory analysis: check for item misfit
```{r}
irt1<-mirt(data1_items,parallel1$nfact)
itemfit(irt1)

```


# Study 2#

```{r}
data2<-read.csv(paste0(workingdir,'/experiment2.csv'))
```

Check time taken
```{r}
cat_time_taken<-mean(data2$cat_questionnaire_time)
seconds_to_period(cat_time_taken/1000)

full_time_taken<-mean(data2$total_time)
seconds_to_period(full_time_taken)


data2_items<-data2[,c('X1','X2','X3','X4','X5','X6','X7','X8','X9','X10','X11','X12','X13','X14','X15','X16','X17','X18','X19','X20','X21','X22','X23','X24','X25')]

```

Do alpha, omega and inter-item and item-total correlations

```{r}
#alpha
psych::alpha(x=data2_items)

#omega
psych::omega(data2_items)

#inter-item correlation
data_correlation4 <- data2_items %>% corrr::correlate() 
data_correlation4 <- data_correlation4 %>% dplyr::select(-rowname) %>% colMeans(na.rm = TRUE)
data_correlation4
mean(data_correlation4)

data.frame(data_correlation4) %>% 
  ggplot2::ggplot(aes(x = data_correlation4)) +
  geom_histogram(bins = 10, alpha = .5) +
  geom_vline(xintercept = mean(data_correlation4), color = "red") +
  xlab("Mean inter-item correlation") +
  theme_bw()

#plot item response distributions
data_melted <- melt(data2_items)
plot<-ggplot(data_melted,aes(x = value, group = variable)) +
geom_bar()
plot+facet_wrap(. ~ variable)

data2_items$score<-rowSums(data2_items)
total_correlation3 <- data2_items %>% corrr::correlate() %>% focus(score)
mean(total_correlation3$score)
```

Run an EFA and explore the best fit

```{r}
data2_items<- data2_items %>% dplyr::select(-'score')

psych::KMO(data2_items)
temp<-round(cor(data2_items),2)
cortest.bartlett(temp,n=nrow(data2_items))

set.seed(456)
parallel2 <- fa.parallel(data2_items, fm = 'minres', fa = 'fa')
parallel2$fa.values

set.seed(123)
parallel2 <- fa.parallel(data2_items, fm = 'minres', fa = 'fa')
parallel2$fa.values

efa2<- fa(data2_items,nfactors = parallel2$nfact,rotate = "oblimin",fm="minres")
print(efa2)
```

Item response theory analysis: check for item misfit
```{r}
irt2<-mirt(data2_items,parallel2$nfact)
itemfit(irt2)
```


# Study 3#
Load in the data

```{r}
data3<-read.csv(paste0(workingdir,'/experiment3.csv'))
```

Check for potential poor responders

```{r}

#check ones and fives and threes
data3_items<-dplyr::select(data3,contains('cata'))
items_used<-apply(data3_items,1,unique)
single_item_responders<-lapply(items_used,length)
single_item_responders<-unlist(single_item_responders)
single_item_responders<-ifelse(single_item_responders==1,1,0)


print('manually inspect data of participants with the following IDS:')
print(which(single_item_responders==1))

```

Quality assurance: We compared the scores on the short version questionnaire items that are in the full version. 
```{r}
#create short table with relevant items from long version questionnaire: 
data3_quality <- data3 %>% dplyr::select('ID', 'cata2', 'cata17', 'cata6')
data3_quality$long_score <- rowSums(data3_quality[,c(2,3,4)])

#create short table with relevant items from short version questionnaire: 
short_cata3_quality <- data3 %>% dplyr::select(c(contains('ID'),contains('short_X')))
short_cata3_quality$short_score <- rowSums(short_cata3_quality[,c(2,3,4)])

#Merge scores by ID: 
short_long_quality <- Reduce(function(x,y) merge(x=x, y=y, by = 'ID'),
                   list(data3_quality,short_cata3_quality))
#Keep only scores: 
short_long_quality <- short_long_quality %>% dplyr::select('long_score','short_score')

#Calculate difference between the two: 
short_long_quality$diff <- abs(short_long_quality$long_score - short_long_quality$short_score)

ggplot(short_long_quality,aes(x=long_score,y=short_score))+
  geom_point()+
  geom_smooth(method='lm')

```



Check how long the total experiment and questionnaire took

```{R}
cat_time_taken<-mean(data3$cat_questionnaire_time)
seconds_to_period(cat_time_taken/1000)

short_time_taken<-mean(data3$short_questionnaire_time)
seconds_to_period(short_time_taken/1000)

full_time_taken<-mean(data3$total_time)
seconds_to_period(full_time_taken)

```
Psychometric analyses of Catastrophising Questionnaire

```{r}
#alpha
psych::alpha(x=data3_items)

#omega
psych::omega(data3_items)

#inter-item correlation
data_correlation3 <- data3_items %>% corrr::correlate() 
data_correlation3 <- data_correlation3 %>% dplyr::select(-rowname) %>% colMeans(na.rm = TRUE)
data_correlation3
mean(data_correlation3)

data.frame(data_correlation3) %>% 
  ggplot2::ggplot(aes(x = data_correlation3)) +
  geom_histogram(bins = 10, alpha = .5) +
  geom_vline(xintercept = mean(data_correlation3), color = "red") +
  xlab("Mean inter-item correlation") +
  theme_bw()

#plot item response distributions
data_melted <- melt(data3_items)
plot<-ggplot(data_melted,aes(x = value, group = variable)) +
geom_bar()
plot+facet_wrap(. ~ variable)

#item-total correlation
data3_items$score<-rowSums(data3_items)
total_correlation3 <- data3_items %>% corrr::correlate() %>% focus(score)
mean(total_correlation3$score)
```

Perform a CFA

```{r}
model<-' factor  =~ cata1 + cata2 + cata3 + cata4 + cata5 + cata6 + cata7 + cata8 + cata9 + cata10 + cata11 + cata12 + cata13 + cata14 + cata15 + cata16 + cata17 + cata18 + cata19 + cata20 + cata21 + cata22 + cata23 + cata24 '

fit<-lavaan::cfa(model=model,data=data3_items)
summary(fit, fit.measures=TRUE)

```

Check reliability of other questionnaires

```{r}
print('STAI')
psych::omega(dplyr::select(data3,contains('STAI')))

print('PHQ')
psych::omega(dplyr::select(data3,contains('PHQ')))

print('GAD')
psych::omega(dplyr::select(data3,contains('GAD')))

print('RRS')
psych::omega(dplyr::select(data3,contains('RRS')))

print('PSWQ')
psych::omega(dplyr::select(data3,contains('PSWQ')))

print('TEPS-ANT')
psych::omega(dplyr::select(data3,contains('teps_ant')))

print('TEPS-CON')
psych::omega(dplyr::select(data3,contains('teps_con')))

print('CDS')
psych::alpha(dplyr::select(data3,contains('cds')))

print('Short')
psych::omega(dplyr::select(data3,c(contains('short_X')))) #the extra bit is needed so don't get the time

```

Now, perform an FA on all questionnaires together (excluding the short version of the Catastrophising Questionnaire)

```{r}
data3_fa<-dplyr::select(data3,c(contains('cata'),contains('rrs'),contains('pswq'),contains('gad'),contains('phq'),contains('stai')))

data3_fa<-data3_fa[,order(colnames(data3_fa))] #put in alphabetical order to replicate graph exactly

parallel <- fa.parallel(data3_fa,fm='minres',fa='fa')
fit<-fa(data3_fa,nfactors=parallel$nfact)
fit


loadings<-data.frame(fit$loadings[])

colnames(loadings)<-c("worry", "catastrophising", "rumination", "trait anxiety", "low mood and anxiety","other1","other2")

names<-c(rep('Catastrophising',24),rep('GAD-7',7),rep('PHQ-9',8),rep('PSWQ',16),rep('RRS',22),c(rep('STAI-T',20)))

names_df<-data.frame(Questionnaire=names)
rownames(names_df) <- rownames(loadings)

ancol<- list(Questionnaire =c('Catastrophising' ="#E41A1C", 'GAD-7' ="#377EB8",'PHQ-9' ="#4DAF4A", 'PSWQ'="#984EA3", 'RRS'='#FF7F00', 'STAI-T'='#FFFF33'))
```

Generate figure 1a (heatmap of factor analysis of all convergent/divergent measures)

```{r}
heatmapplot <- pheatmap(
  mat               = loadings,
  border_color      = NA,
  color             = colorRampPalette(c("blue4", "white", "firebrick1"))(100),
  cellwidth         = 70,
  cellheight        = 3,
  show_colnames     = TRUE,
  show_rownames     = FALSE,
  drop_levels       = TRUE,
  fontsize          = 14,
  main              = "Factors",
  treeheight_row    = 0, 
  treeheight_col    = 0,
  cluster_rows      = FALSE,
  annotation_row    = names_df,
  annotation_colors = ancol,
  angle_col         = 90,
  gaps_col          = c(1,2),
  width             = 5, 
  height            = 5
)

if (save_images==1){
  ggsave(heatmapplot,filename=paste0(workingdir,'/fa_heatmap.png'),width=12,height=9)
}


```

Generate figure 1b (heatmap of correlations between all questionnaires)

```{r}
Cat<-rowSums(dplyr::select(data3,contains('cata')))
scores<-data.frame(Cat)
scores$STAI<-rowSums(dplyr::select(data3,contains('STAI')))
scores$PHQ<-rowSums(dplyr::select(data3,contains('PHQ')))
scores$GAD<-rowSums(dplyr::select(data3,contains('GAD')))
scores$RRS<-rowSums(dplyr::select(data3,contains('RRS')))
scores$PSWQ<-rowSums(dplyr::select(data3,contains('PSWQ')))
scores$TEPS_ANT<-rowSums(dplyr::select(data3,contains('teps_ant')))
scores$TEPS_CON<-rowSums(dplyr::select(data3,contains('teps_con')))
scores$CDS<-rowSums(dplyr::select(data3,contains('cds')))
scores$short_cat<-rowSums(dplyr::select(data3,c(contains('short_X')))) #the extra bit is needed so don't get the time

cormat <- round(cor(scores),2)
melted_cormat <- melt(cormat)
melted_cormat$Var1<-factor(melted_cormat$Var1,ordered=TRUE,levels=c('Cat','short_cat','CDS','GAD','PHQ','PSWQ','RRS','STAI','TEPS_ANT','TEPS_CON'))
melted_cormat$Var2<-factor(melted_cormat$Var2,ordered=TRUE,levels=c('Cat','short_cat','CDS','GAD','PHQ','PSWQ','RRS','STAI','TEPS_ANT','TEPS_CON'))

corrplot<-ggplot(data = melted_cormat, aes(x=Var2, y=Var1, fill=value)) + 
  geom_tile()+
  scale_fill_gradient2(midpoint = 0, low = "navy", mid = "white", high = "red")+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)+
  labs(fill='correlation \n coefficient')+
  theme(axis.title=element_blank(),text=element_text(size=16))

if (save_images==1){
  ggsave(corrplot,filename=paste0(workingdir,'/questionnaire_correlations.png'),width=12,height=9)
}

```

Simple correlations between Catastrophising questionnaire and convergent/divergent validity measures, along with p values

```{r}
scores$short_cat_3item<-rowSums(dplyr::select(data3,c('short_X1.quantised','short_X2.quantised','short_X3.quantised')))
cor.test(scores$Cat,scores$short_cat)
cor.test(scores$Cat,scores$short_cat_3item)
cor.test(scores$Cat,scores$CDS)
cor.test(scores$Cat,scores$GAD)
cor.test(scores$Cat,scores$PHQ)
cor.test(scores$Cat,scores$PSWQ)
cor.test(scores$Cat,scores$RRS)
cor.test(scores$Cat,scores$STAI)
cor.test(scores$Cat,scores$TEPS_ANT)
cor.test(scores$Cat,scores$TEPS_CON)

cor.test(scores$CDS,scores$STAI)
cor.test(scores$CDS,scores$PSWQ)
```
Discriminant validity analysis with TEPS

```{r}
model<-'catastrophising =~  cata1 + cata2 + cata3 + cata4 + cata5 + cata6 + cata7 + cata8 + cata9 + cata10 + cata11 + cata12 + cata13 + cata14 + cata15 + cata16 + cata17 + cata18 + cata19 + cata20 + cata21 + cata22 + cata23 + cata24

teps_a =~  teps_ant_response.11.quantised + teps_ant_response.12.quantised + teps_ant_response.14.quantised + teps_ant_response.16.quantised + teps_ant_response.17.quantised + teps_ant_response.19.quantised + teps_ant_response.2.quantised + teps_ant_response.5.quantised + teps_ant_response.7.quantised  + teps_ant_response.9.quantised 

teps_c =~ teps_con_response.10.quantised + teps_con_response.13.quantised + teps_con_response.15.quantised + teps_con_response.18.quantised + teps_con_response.3.quantised + teps_con_response.4.quantised + teps_con_response.6.quantised + teps_con_response.8.quantised

'

dat <- data3 %>% dplyr::select(c(contains('cata')),contains('teps_'))
htmt(model, dat)
```


Incremental validity analysis 
```{r}
data3_scores<-data.frame(scores,
                         diagnosis_general=data3$diagnosis_general,
                         diagnosis_anxdep=data3$diagnosis_anxdep,
                         medication_general=data3$medication_general,
                         medication_anxdep=data3$medication_anxdep)

model1<-glm(diagnosis_general ~ PHQ + GAD, data=data3_scores, family=binomial)
model2<-glm(diagnosis_general ~ PHQ + GAD + Cat, data=data3_scores, family=binomial)
anova(model1,model2, test ="Chisq")

model1<-glm(diagnosis_anxdep ~ PHQ + GAD, data=data3_scores, family=binomial)
model2<-glm(diagnosis_anxdep ~ PHQ + GAD + Cat, data=data3_scores, family=binomial)
anova(model1,model2, test ="Chisq")

#multinomial for medication status

data3_scores$medication_general <- relevel(data3_scores$medication_general, ref = "No")
test1 <- multinom(medication_general ~ PHQ + GAD, data = data3_scores)
test2 <- multinom(medication_general ~ PHQ + GAD + Cat, data = data3_scores)
anova(test1,test2)


data3_scores$medication_anxdep <- relevel(data3_scores$medication_anxdep, ref = "No")
test1 <- multinom(medication_anxdep ~ PHQ + GAD, data = data3_scores)
test2 <- multinom(medication_anxdep ~ PHQ + GAD + Cat, data = data3_scores)
anova(test1,test2)
```

Create figure 2 raincloud plots of difference in scores between diagnoses/medication
```{r}

data3_scores$medication_general<-recode(data3_scores$medication_general,"'No'= 1;'Yes I took medication in the past'=2;'Yes I currently take medication'= 3")
data3_scores$medication_anxdep<-recode(data3_scores$medication_anxdep,"'No'= 1;'Yes I took medication in the past'=2;'Yes I currently take medication'= 3")

data3_scores$diagnosis_general<-ifelse(data3_scores$diagnosis_general=='yes',2,1)
data3_scores$diagnosis_anxdep<-ifelse(data3_scores$diagnosis_anxdep=='yes',2,1)

data3_scores$diagnosis_general<-factor(data3_scores$diagnosis_general)
data3_scores$diagnosis_anxdep<-factor(data3_scores$diagnosis_anxdep)
data3_scores$medication_general<-factor(data3_scores$medication_general)
data3_scores$medication_anxdep<-factor(data3_scores$medication_anxdep)


a<-ggplot(data=data3_scores,aes(x=diagnosis_general,y=Cat,fill=diagnosis_general)) + 
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, trim = FALSE)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_boxplot(aes(x = as.numeric(diagnosis_general)+0.25, y = Cat),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  labs(y='Catastrophising Score',x='History of any mental illness') + 
  scale_fill_manual(values= c("#00AFBB", "#E7B800","#FC4E07"))+
  scale_x_discrete(breaks=c(1,2),labels=c('No','Yes'))+
  theme_classic()+
  theme(legend.position='none')

b<-ggplot(data=data3_scores,aes(x=diagnosis_anxdep,y=Cat,fill=diagnosis_anxdep)) + 
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, trim = FALSE)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_boxplot(aes(x = as.numeric(diagnosis_anxdep)+0.25, y = Cat),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  labs(y='Catastrophising Score',x='History of anxiety or depression') + 
  scale_fill_manual(values= c("#00AFBB", "#E7B800","#FC4E07"))+
  scale_x_discrete(breaks=c(1,2),labels=c('No','Yes'))+
  theme_classic()+
  theme(legend.position='none')

c<-ggplot(data=data3_scores,aes(x=medication_general,y=Cat,fill=medication_general)) + 
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, trim = FALSE)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_boxplot(aes(x = as.numeric(medication_general)+0.25, y = Cat),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  labs(y='Catastrophising Score',x='History of any psychiatric medication use') + 
  scale_fill_manual(values= c("#00AFBB", "#E7B800","#FC4E07"))+
  scale_x_discrete(breaks=c(1,2,3),labels=c('No','Yes, formerly','Yes, currently'))+
  theme_classic()+
  theme(legend.position='none')


d<-ggplot(data=data3_scores,aes(x=medication_anxdep,y=Cat,fill=medication_anxdep)) + 
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, trim = FALSE)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_boxplot(aes(x = as.numeric(medication_anxdep)+0.25, y = Cat),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  labs(y='Catastrophising Score',x='History of medication use for anxiety or depression') + 
  scale_x_discrete(breaks=c(1,2,3),labels=c('No','Yes, formerly','Yes, currently'))+
  scale_fill_manual(values= c("#00AFBB", "#E7B800","#FC4E07"))+
  theme_classic()+
  theme(legend.position='none')

plot_grid(a,b,c,d,labels='AUTO')
if (save_images==1){
  ggsave(file=paste0(workingdir,'/raincloud_plots.png'),height=9,width=12)
}

```
Now analyse using SEM

```{r}
model<- '
  #latent variable definitions
  catastrophising =~ cata1 + cata2 + cata3 + cata4 + cata5 + cata6 + cata7 + cata8 + cata9 + cata10 + cata11 + cata12 + cata13
  + cata14  +  cata15 + cata16 + cata17 + cata18 + cata19 + cata20 + cata21 + cata22 + cata23 + cata24
  
  trait_anx=~ stai_response.2.quantised + stai_response.3.quantised + stai_response.4.quantised + stai_response.5.quantised + 
  stai_response.6.quantised + stai_response.7.quantised + stai_response.8.quantised + stai_response.9.quantised + 
  stai_response.10.quantised + stai_response.11.quantised + stai_response.12.quantised + stai_response.13.quantised + 
  stai_response.14.quantised + stai_response.15.quantised + stai_response.16.quantised + stai_response.17.quantised +         
  stai_response.18.quantised + stai_response.19.quantised + stai_response.20.quantised + stai_response.21.quantised
  
  gad=~gad7_response.1.quantised + gad7_response.2.quantised + gad7_response.3.quantised + gad7_response.4.quantised+
  gad7_response.5.quantised + gad7_response.6.quantised + gad7_response.7.quantised
  
  worry=~ pswq_response.2.quantised + pswq_response.3.quantised + pswq_response.4.quantised + pswq_response.5.quantised + 
  pswq_response.6.quantised + pswq_response.7.quantised + pswq_response.8.quantised + pswq_response.9.quantised +
  pswq_response.10.quantised + pswq_response.11.quantised + pswq_response.12.quantised + pswq_response.13.quantised +
  pswq_response.14.quantised + pswq_response.15.quantised + pswq_response.16.quantised + pswq_response.17.quantised
  
  depression=~phq9_response.1.quantised + phq9_response.2.quantised + phq9_response.3.quantised + phq9_response.4.quantised + 
  phq9_response.5.quantised + phq9_response.6.quantised + phq9_response.7.quantised + phq9_response.8.quantised

  
  rumination=~rrs_response.2.quantised + rrs_response.3.quantised + rrs_response.4.quantised + rrs_response.5.quantised + 
  rrs_response.6.quantised + rrs_response.7.quantised + rrs_response.8.quantised + rrs_response.9.quantised + 
  rrs_response.10.quantised + rrs_response.11.quantised + rrs_response.12.quantised + rrs_response.13.quantised + 
  rrs_response.14.quantised + rrs_response.15.quantised + rrs_response.16.quantised + rrs_response.17.quantised +         
  rrs_response.18.quantised + rrs_response.19.quantised + rrs_response.20.quantised + rrs_response.21.quantised +
  rrs_response.22.quantised + rrs_response.23.quantised
  
'
  
fit <- cfa(model, data=data3)
covariances<-lavInspect(fit,what='cor.lv')
covariances <- round(covariances,2)
cov_long<-melt(covariances)
semplot<-ggplot(data = cov_long, aes(x=Var2, y=Var1, fill=value)) + 
  geom_tile()+
  scale_fill_gradient2(midpoint = 0, low = "navy", mid = "white", high = "red")+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)+
  theme(axis.title=element_blank())+
  labs(fill='correlation \n coefficient')

if (save_images==1){
  ggsave(semplot,filename=paste0(workingdir,'/sem_correlations.png'),width=12,height=9)
}
```


# Study 4#

Load data

```{r}

data4<-read.csv(paste0(workingdir,'/experiment4.csv'))
```

Time taken

```{r}
cat_time_taken_t1<-mean(data4$cat_questionnaire_time_t1)
seconds_to_period(cat_time_taken_t1/1000)

cat_time_taken_t2<-mean(data4$cat_questionnaire_time_t2)
seconds_to_period(cat_time_taken_t2/1000)

full_time_taken<-mean(data4$total_time)
seconds_to_period(full_time_taken)
```



Test-retest correlation and plot
```{r}
cor(data4$score_t1,data4$score_t2)
cor.test(data4$score_t1,data4$score_t2)

#function for getting the regression equation as text
lm_eqn <- function(x,y){
    m <- lm(y ~ x);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}


ggplot(data=data4,aes(x=score_t1,y=score_t2))+
  geom_point()+
  labs(x='Score time 1',y='Score time 2')+
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x)+
  geom_text(x = 35, y = 100, label = lm_eqn(data4$score_t1,data4$score_t2), parse = TRUE)


```

Calculate ICC (A,1) and (C,1) for absolute agreement and consistency (runs two-way mixed ICC analyses)

```{r}
icc_a1<-irr::icc(cbind(data4$score_t1,data4$score_t2),model = "twoway",
    type = "agreement",
    unit = "single", 
    r0 = 0,
    conf.level = 0.95)

icc_a1

icc_c1<-irr::icc(cbind(data4$score_t1,data4$score_t2),model = "twoway",
    type = "consistency",
    unit = "single", 
    r0 = 0,
    conf.level = 0.95)

icc_c1
```

Alpha, omega, inter-item and item-total correlations

```{r}
data4_items<-dplyr::select(data4,contains('t2'))%>%dplyr::select(contains('X'))

#alpha
psych::alpha(x=data4_items)

#omega
psych::omega(data4_items)

#inter-item correlation
data_correlation4 <- data4_items %>% corrr::correlate() 
data_correlation4 <- data_correlation4 %>% dplyr::select(-rowname) %>% colMeans(na.rm = TRUE)
data_correlation4
mean(data_correlation4)

data.frame(data_correlation4) %>% 
  ggplot2::ggplot(aes(x = data_correlation4)) +
  geom_histogram(bins = 10, alpha = .5) +
  geom_vline(xintercept = mean(data_correlation4), color = "red") +
  xlab("Mean inter-item correlation") +
  theme_bw()

#item-total correlation
data4_items$score<-rowSums(data4_items)
total_correlation4 <- data4_items %>% corrr::correlate() %>% corrr::focus(score)
mean(total_correlation4$score)
```
CFA

```{r}
data4_items<- data4_items %>% dplyr::select(-'score')

model<-' catastrophising  =~ X1_t2 + X2_t2 + X3_t2 + X4_t2 + X5_t2 + X6_t2 + X7_t2 + X8_t2 + X9_t2 + X10_t2 + X11_t2 + X12_t2 + X13_t2 + X14_t2 + X15_t2 + X16_t2 + X17_t2 + X18_t2 + X19_t2 + X20_t2 + X21_t2 + X22_t2 + X23_t2 + X24_t2 '

fit<-lavaan::cfa(model=model,data=data4_items)
summary(fit, fit.measures=TRUE)
```

# Study 5#

Load data

```{r}

data5<-read.csv(paste0(workingdir,'/experiment5.csv'))
```


Alpha, omega, inter-item and item-total correlations

```{r}
data5_items<-dplyr::select(data5,contains('cat'))

#alpha
psych::alpha(x=data5_items)

#omega
psych::omega(data5_items)

#inter-item correlation
data_correlation5 <- data5_items %>% corrr::correlate() 
data_correlation5 <- data_correlation5 %>% dplyr::select(-rowname) %>% colMeans(na.rm = TRUE)
data_correlation5
mean(data_correlation5)

data.frame(data_correlation5) %>% 
  ggplot2::ggplot(aes(x = data_correlation5)) +
  geom_histogram(bins = 10, alpha = .5) +
  geom_vline(xintercept = mean(data_correlation5), color = "red") +
  xlab("Mean inter-item correlation") +
  theme_bw()

#item-total correlation
data5_items$score<-rowSums(data5_items)
total_correlation5 <- data5_items %>% corrr::correlate() %>% corrr::focus(score)
mean(total_correlation5$score)
```
Run CFA

```{r}
data5_items<- data5_items %>% dplyr::select(-'score')

model<-' catastrophising  =~ cat_X18.quantised + cat_X4.quantised + cat_X21.quantised + cat_X1.quantised + cat_X10.quantised + cat_X14.quantised + cat_X15.quantised + cat_X6.quantised + cat_X3.quantised + cat_X24.quantised + cat_X9.quantised + cat_X22.quantised + cat_X7.quantised + cat_X19.quantised + cat_X8.quantised + cat_X16.quantised + cat_X23.quantised + cat_X11.quantised + cat_X13.quantised + cat_X5.quantised + cat_X12.quantised + cat_X20.quantised + cat_X2.quantised + cat_X17.quantised '

fit<-lavaan::cfa(model=model,data=data5_items)
summary(fit, fit.measures=TRUE)
```


Correlations between discriminant measures and catastrophising

```{r}
#psychometrics of discriminant measures
psych::omega(dplyr::select(data5,contains('au_')))
psych::omega(dplyr::select(data5,contains('ss.ue_')))
psych::omega(dplyr::select(data5,contains('ss.cd_')))
psych::omega(dplyr::select(data5,contains('ss.ia_')))
psych::omega(dplyr::select(data5,contains('ss.in_')))


data5$cat.score<-rowSums(dplyr::select(data5,contains('cat_')))
data5$audit.score<-rowSums(dplyr::select(data5,contains('au_')))
data5$schizotypy.ue<-rowSums(dplyr::select(data5,contains('ss.ue_')))
data5$schizotypy.cd<-rowSums(dplyr::select(data5,contains('ss.cd_')))
data5$schizotypy.ia<-rowSums(dplyr::select(data5,contains('ss.ia_')))
data5$schizotypy.in<-rowSums(dplyr::select(data5,contains('ss.in_')))

cor.test(data5$cat.score,data5$audit.score)

model<-'catastrophising =~ cat_X1.quantised + cat_X2.quantised + cat_X3.quantised + cat_X4.quantised + cat_X5.quantised + cat_X6.quantised + cat_X7.quantised + cat_X8.quantised + cat_X9.quantised + cat_X10.quantised + cat_X11.quantised + cat_X12.quantised + cat_X13.quantised + cat_X14.quantised + cat_X15.quantised + cat_X16.quantised + cat_X17.quantised + cat_X18.quantised + cat_X19.quantised + cat_X20.quantised + cat_X21.quantised + cat_X22.quantised + cat_X23.quantised + cat_X24.quantised

alcohol =~ au_response.2.quantised + au_response.3.quantised + au_response.4.quantised + au_response.5.quantised + au_response.6.quantised + au_response.7.quantised + au_response.8.quantised + au_response.9.quantised + au_response.10.quantised + au_response.11.quantised '

dat <- data5 %>% dplyr::select(c(contains('cat_')),contains('au_'))
htmt(model, dat)

cor.test(data5$cat.score,data5$schizotypy.ue)
cor.test(data5$cat.score,data5$schizotypy.cd)
cor.test(data5$cat.score,data5$schizotypy.ia)
cor.test(data5$cat.score,data5$schizotypy.in)


model<-'catastrophising =~ cat_X1.quantised + cat_X2.quantised + cat_X3.quantised + cat_X4.quantised + cat_X5.quantised + cat_X6.quantised + cat_X7.quantised + cat_X8.quantised + cat_X9.quantised + cat_X10.quantised + cat_X11.quantised + cat_X12.quantised + cat_X13.quantised + cat_X14.quantised + cat_X15.quantised + cat_X16.quantised + cat_X17.quantised + cat_X18.quantised + cat_X19.quantised + cat_X20.quantised + cat_X21.quantised + cat_X22.quantised + cat_X23.quantised + cat_X24.quantised

ue =~ ss.ue_response.2.quantised + ss.ue_response.3.quantised + ss.ue_response.4.quantised + ss.ue_response.5.quantised + ss.ue_response.6.quantised + ss.ue_response.7.quantised + ss.ue_response.8.quantised + ss.ue_response.9.quantised + ss.ue_response.10.quantised + ss.ue_response.11.quantised + ss.ue_response.12.quantised + ss.ue_response.13.quantised

cd =~  ss.cd_response.16.quantised + ss.cd_response.17.quantised + ss.cd_response.18.quantised + ss.cd_response.19.quantised + ss.cd_response.20.quantised + ss.cd_response.21.quantised + ss.cd_response.22.quantised + ss.cd_response.23.quantised + ss.cd_response.24.quantised

ia =~ ss.ia_response.27.quantised + ss.ia_response.28.quantised + ss.ia_response.29.quantised + ss.ia_response.30.quantised + ss.ia_response.31.quantised + ss.ia_response.32.quantised + ss.ia_response.33.quantised + ss.ia_response.34.quantised + ss.ia_response.35.quantised + ss.ia_response.36.quantised

inoncompuls =~ ss.in_response.39.quantised + ss.in_response.40.quantised + ss.in_response.41.quantised + ss.in_response.42.quantised  + ss.in_response.43.quantised + ss.in_response.44.quantised + ss.in_response.45.quantised + ss.in_response.46.quantised + ss.in_response.47.quantised + ss.in_response.48.quantised

'

dat <- data5 %>% dplyr::select(c(contains('cat_')),contains('ss.'))
htmt(model, dat)

```
Add plot

```{r}
Cat<-rowSums(dplyr::select(data5,contains('cat_')))
scores<-data.frame(Cat)
scores$STAI<-data5$STAI.score
scores$PHQ<-data5$PHQ.score
scores$GAD<data5$GAD.score
scores$RRS<-data5$RRS.score
scores$PSWQ<-data5$PSWQ.score
scores$AUDIT<-rowSums(dplyr::select(data5,contains('au_')))
scores$UE<-rowSums(dplyr::select(data5,contains('ss.ue_')))
scores$CD<-rowSums(dplyr::select(data5,contains('ss.cd_')))
scores$IA<-rowSums(dplyr::select(data5,contains('ss.ia_')))
scores$IN<-rowSums(dplyr::select(data5,contains('ss.in_')))

cormat <- round(cor(scores),2)
melted_cormat <- melt(cormat)
melted_cormat$Var1<-factor(melted_cormat$Var1,ordered=TRUE,levels=c('Cat','GAD','PHQ','PSWQ','RRS','STAI','AUDIT','UE','CD','IA','IN'))
melted_cormat$Var2<-factor(melted_cormat$Var2,ordered=TRUE,levels=c('Cat','GAD','PHQ','PSWQ','RRS','STAI','AUDIT','UE','CD','IA','IN'))

correlations_q5<-ggplot(data = melted_cormat, aes(x=Var2, y=Var1, fill=value)) + 
  geom_tile()+
  scale_fill_gradient2(midpoint = 0, low = "navy", mid = "white", high = "red")+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)+
  labs(fill='correlation \n coefficient')+
  theme(axis.title=element_blank())

if (save_images==1){
  ggsave(correlations_q5,filename=paste0(workingdir,'/study5_questionnaire_correlations.png'),width=12,height=9)
}
```
